Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-02-17 article.tex
Significant revisions
Two major points of paper: 1) pressure-regulated flow systems outperform syringe pumps 2) Evaluating LSCI vs. MESI using pressure-regulated flow system

\title{Improved fluid phantom for accurate relative flow calculations for speckle contrast imaging}

@@

One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with in vivo absolute flow velocities in animal studies \cite{Kazmi:2013hp}. Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range. Additionally, several instrumentation factors, namely, illumination variations and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making. An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}. MESI has been shown to be reliable for chronic imaging and to have high correlation with in vivo absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons. By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.

@@

\subsection{Microfluidic Phantom Fabrication}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microchannel, shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the microfluidic channel. A square cross-section (1:1 aspect ratio) was desired to match the aspect ratio of the circular cross-section vascular geometries in vivo. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was used to connect to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow sensor and the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end submerged in solution. A photograph of the finished phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS and the glass slide seals the surface.

@@

To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel. A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system}a. The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) recorded the absolute flow rate.

The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution. The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output (10 mL = 14.5 mm). It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with blood-mimicking solution. Prior to running the desired flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.

Two stepped flow profile experiments were conducted to assess each flow system. First, a 3-step flow profile was used to determine the uncertainty of each flow control system. The experiment lasted 240 seconds, beginning with 30 seconds of no flow (0 mm/s) followed by one full minute at each flow speed (2.4, 3.6, and 4.8 mm/s) before concluding with an additional 30 seconds of no flow. The experiment was repeated three times on each system. The second flow profile experiment consisted of a 13-step flow profile. The flow speed was once again varied from 2.4 to 4.8 mm/s, however in smaller 0.2 mm/s increments. As with the first experiment, the flow profile begins and ends with 30 seconds of no flow, with one full minute at each programmed flow speed (840 seconds total duration). The second experiment was also repeated three times on each flow control system.

To quantify and compare each system, we calculated the total combined uncertainty in accordance with National Institute of Standards and Technology (NIST) guidelines \cite{Taylor.199438,NIST:2002}. Three main sources of uncertainty were identified for inclusion in the uncertainty budget: repeatability, reproducibility, and measurement bias. Standard uncertainties were calculated for each flow step using 55 seconds of data, allowing for 5 seconds of transition from the previous flow state. All values were expressed as percentages relative to their respective means.

@@

@@

A schematic of the imaging setup is shown in Fig.~\ref{fig:system}a. MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.). The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.). The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance. Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam. The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the sample.

A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG). Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm. The camera exposures were temporally synchronized with the modulated laser pulses. Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of $\sim$2.5 frames-per-second (fps). The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The entire acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

% Figure 2 - System Schematic
\begin{figure}
    \includegraphics[width=\textwidth]{Figure2.pdf}
    \caption {
        (a) Optical system schematic for microfluidic flow assessment. A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements. Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system. The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
    }
    \label{fig:system}
\end{figure}

\subsection{MESI Microfluidic Flow Measurements}

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of MESI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step. The experiment was repeated a total of four times across two days.

Raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) using a 7$\times$7-pixel sliding window. The average speckle contrast of each frame was then calculated within a region centered in the microfluidic channel and used to estimate the correlation time ($\tau_c$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast values were fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} using all fifteen exposure times to obtain $\tau_c$:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}

\noindent where $T$ is the camera exposure time, $x=T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu$ represents exposure-independent instrument noise and nonergodic variances. $\beta$ was held constant at all timepoints by performing an initial fit to Eq. 3 using the median speckle contrast value at each exposure across the entire multi-exposure dataset. All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.). The resulting $\tau_c$ estimates were smoothed temporally using a central moving average filter ($k=5$).

Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used to visualize measurements. In order to directly compare the MESI measurements with the flow sensor, the relative flow was calculated using the average value of the 1 mm/s step as the baseline ($rICT = ICT/ICT_\textnormal{1mm/s}$). The average value of each flow step was calculated using 115 seconds of data, allowing for 5 seconds of transition from the previous step.

@@

A comparison between the measured flow speeds of the syringe pump and the pressure-regulated flow system is shown in Fig.~\ref{fig:syringe_vs_pressure}. From these plots, we observe that the pressure-regulated system outperforms the syringe pump system by accurately and steadily reaching the programmed flow speeds in both experiments. While both systems quickly responded to the desired flow changes (Fig.~\ref{fig:syringe_vs_pressure}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system. Furthermore, the small flow step experiment (Fig.~\ref{fig:syringe_vs_pressure}b) demonstrated that the syringe pump system cannot reliably produce finer flow changes as seen by the loss of the stair-stepped flow pattern.

% Figure 3 - Syringe Pump vs. Pressure System
\begin{figure}
    \includegraphics[width=\textwidth]{Figure3.pdf}
    \caption {
        Flow profiles for the syringe pump (blue) and pressure-regulated (red) flow systems compared to the ideal programmed flow (black) for one run of the (a) 3-step and (b) 13-step experiments. The microfluidic flow speed varied between 2.4 to 4.8 mm/s in 1.2 mm/s and 0.2 mm/s steps for the 3- and 13-step experiments, respectively.
    }
    \label{fig:syringe_vs_pressure}
\end{figure}

Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiment. These results confirm the observations from Fig.~\ref{fig:syringe_vs_pressure} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds. The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}. These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes. With the syringe pump system, it would be impossible to reliably separate changes in relative flow of 20\% from flow system noise at the 2.4 mm/s flow speed. This magnitude of uncertainty in flow generation would make it difficult to assess an optical system’s ability to detect small changes in flow. This limitation is visually represented in Fig.~\ref{fig:syringe_vs_pressure}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes. Using the pressure-regulated flow system, we can confidently design experiments with relative flow changes of only 1.5\% and be certain that the resulting optical system measurements are not due to flow system noise. Furthermore, this would allow for the assessment of improvements to optical system performance at this scale.

@@

\subsection{MESI Microfluidic Flow Measurements}

The MESI microfluidic flow measurements using only the pressure-regulated flow system are shown in Fig.~\ref{fig:mesi_flow}. The relative flow measured by MESI ($rICT$) is plotted alongside the relative flow sensor measurements from a single trial in Fig.~\ref{fig:mesi_flow}a. Both metrics were calculated using the average of the first flow step (1 mm/s) as the baseline. Data for each flow step were pooled and averaged across all four trials to assess the overall performance of MESI as seen in Fig.~\ref{fig:mesi_flow}b. The coefficient of determination ($R^2$) and concordance correlation coefficient ($\rho_c$) \cite{Lin.1989} were 0.988 and 0.994, respectively, indicating strong agreement between the MESI $rICT$ and the flow sensor measurements. The absolute MESI $ICT$ measurements are also plotted on Fig.~\ref{fig:mesi_flow}b and exhibit the same linearity with microfluidic flow speed.

% Figure 4 - MESI Flow Measurements
\begin{figure}
    \includegraphics[width=\textwidth]{Figure4.pdf}
    \caption {
        (a) Relative flow profiles for the flow sensor (black) and MESI (red) for one trial, both normalized to the average of the first flow step (1 mm/s). (b) Performance of MESI flow estimates (relative and absolute) compared to measured microfluidic flow speed aggregated across all four trials (mean $\pm$ sd). The dashed line denotes the line of equality indicative of a 1:1 relationship.
    }
    \label{fig:mesi_flow}
\end{figure}

Fig.~\ref{fig:mesi_error} presents the percent error for the MESI measurements at each flow step aggregated across all four trials. The absolute error was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it almost doubled in value.

>>>>

\title{Using pressure-driven flow systems to evaluate laser speckle contrast imaging}

@@

One of the primary limitations of LSCI is the difficulty to accurately provide a quantitative assessment of flow, as demonstrated by its weak correlation with \textit{in vivo} absolute flow velocities in animal studies \cite{Kazmi:2013hp}. Standard LSCI systems use a single camera exposure time, limiting flow sensitivity to a small range. Additionally, several instrumentation factors, namely, illumination variations and noise across different imaging sessions, limits LSCI to intra-patient usage at a single time point and prevents LSCI from providing the quantitative flow data that would be necessary to assist in surgical decision-making. An extension to LSCI called multi-exposure speckle imaging (MESI) has been developed that improves upon many of the shortcomings of LSCI, especially the quantitative accuracy \cite{Parthasarathy:2008el}. MESI has been shown to be reliable for chronic imaging and to have high correlation with \textit{in vivo} absolute velocities in animal studies \cite{Kazmi:2013hp}, suggesting potential for accurate intra- and inter-patient comparisons. By using multiple camera exposure times spanning multiple decades and a more robust mathematical model to estimate flow velocity, the MESI technique has higher accuracy and sensitivity compared to LSCI \cite{Parthasarathy:2008el}.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) per gram of PDMS added to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was used to connect to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow sensor and the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end submerged in solution. A photograph of the finished phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS and the glass slide seals the surface.

@@

To assess the performance of the syringe pump and pressure-regulated flow systems, and to quantify the uncertainty of each system, it is necessary to know the true flow rate of the blood-mimicking solution through the microfluidic channel. A mass flow sensor (FLU-L, 0 -- 1 mL/min, Fluigent, Inc.) was placed inline between the flow control system and the phantom inlet tubing, as shown in Fig.~\ref{fig:system_lsci}a. The sensor was connected to a flow reader (Flow Board, FLB, Fluigent, Inc.) to digitize the sensor output and the MAESFLO software (Fluigent, Inc.) was used to record the absolute flow rate. All flow sensor measurements were downsampled from 10 Hz to 2 Hz using interpolation to match the timing of the optical measurements.

The syringe pump system (74905-04, Cole-Parmer Instrument Company, LLC.) was connected to the flow sensor, as shown in Fig.~\ref{fig:system_lsci}b, and a 10 mL plastic syringe (BD \#302149) was filled with blood-mimicking solution as described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run the desired flow profile, using the inner diameter of the syringe to ensure correct flow rate output. It should be noted that a 3 mL syringe was also tested, however its performance was significantly worse than the 10 mL syringe and, in some cases, could not resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller base unit (MFCS-EZ with 69 mbar channel, Fluigent, Inc.), powered by a house air line regulated to maintain 500 mbar of pressure, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The pressure control system used built-in software (MAESFLO) to provide feedback from the inline flow sensor to regulate the pressure to achieve the desired flow rate.

% Figure 2 - LSCI System Schematic + Syringe Pump and Pressure Flow System
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure2.pdf}
    \caption {
        (a) LSCI system schematic for microfluidic flow assessment. A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements. Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system. The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
    }
    \label{fig:system_lsci}
\end{figure}

\subsection{Microfluidic Flow System Assessment}
\label{sect:methods_flow_assess}

Two stepped flow profile experiments were conducted to assess each flow system using the commercial flow sensor. First, a 3-step flow profile was used to determine the uncertainty of each flow control system. The experiment lasted 240 seconds, beginning with 30 seconds of no flow (0 mm/s) followed by one full minute at each flow speed (2.4, 3.6, and 4.8 mm/s) before concluding with an additional 30 seconds of no flow. The experiment was repeated three times on each system. The second flow profile experiment consisted of a 13-step flow profile. The flow speed was once again varied from 2.4 to 4.8 mm/s, however in smaller 0.2 mm/s increments. As with the first experiment, the flow profile begins and ends with 30 seconds of no flow, with one full minute at each programmed flow speed (840 seconds total duration). The second experiment was also repeated three times on each flow control system.

To quantify and compare each flow system, we calculated the total combined uncertainty in accordance with National Institute of Standards and Technology (NIST) guidelines \cite{Taylor.199438,NIST:2002}. Three main sources of uncertainty were identified for inclusion in the uncertainty budget: repeatability, reproducibility, and measurement bias. Standard uncertainties were calculated for each flow step using 55 seconds of data, allowing for 5 seconds of transition from the previous flow state. All values were expressed as percentages relative to their respective means.

@@

\subsection{LSCI Instrumentation}

A schematic of the LSCI setup is shown in Fig.~\ref{fig:system_lsci}a. Measurements were performed using a 660 nm laser diode (HL6545MG, Thorlabs Inc.) mounted in a temperature-controlled housing (LDM21, Thorlabs Inc.) and expanded using an aspheric lens to obliquely illuminate the microfluidic. The laser diode controller (LDC205C, Thorlabs, Inc.) was set to 200 mA ($\sim$120 mW) while the temperature controller (TED200C, Thorlabs Inc.) was set to 10.5 k$\Omega$ (23.8 $^\circ$C). A pair of fixed focal length consumer camera lenses (AF Nikkor 50 mm $f$/1.8D, Nikon Corp.) were placed in tandem with infinity focus for 1:1 imaging. \textcolor{red}{Is there a filter? Specifics of f-number and speckle size?} The scattered light was imaged with a CCD camera (piA640-210gm, 648 $\times$ 488 pixels, Basler AG) controlled using custom software written in C++. The full sensor array was used, resulting in a field-of-view of 4.8 $\times$ 3.6 mm. The camera exposure time was set to 0.5 ms and allowed to run at full speed, resulting in an effective acquisition rate of $\sim$150 frames-per-second (fps). \textcolor{red}{Explanation for 0.5 ms exposure time?}

\subsection{LSCI Flow Measurements}
\label{sect:methods_lsci}

To validate the flow sensor measurements, single-exposure LSCI was used to simultaneously image the microfluidic flow phantom during the 13-step flow experiments described in Section \ref{sect:methods_flow_assess}. Raw intensity images were converted to speckle contrast images using Eq. \ref{eq:sc}, where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) in a sliding 7$\times$7-pixel window centered at every pixel.
%
% Equation 4 - Speckle Contrast
\begin{equation}
    \label{eq:sc}
    K = \frac{\sigma_{s}}{\langle{I}\rangle}
\end{equation}

By incorporating efficient processing techniques\cite{Tom:2008tg} into the acquisition software, speckle contrast images were computed, displayed, and saved in real-time. \textcolor{red}{Unclear if there was additional averaging performed by the Speckle Software (i.e. frames/sequence=15? Was the saved SC data already averaged?)} During post-processing, the average speckle contrast was extracted from each frame within a region centered in the microfluidic channel. This value was used to estimate the correlation time ($\tau_{c}$) of the speckle autocorrelation function, which is considered a more quantitative measure of flow \cite{Briers:1996kfa}. The averaged speckle contrast value at each timepoint was fitted for its corresponding $\tau_{c}$ using Eq. \ref{eq:lsci},
%
% Equation 5 - LSCI Equation
\begin{equation}
    \label{eq:lsci}
    K^2(T, \tau_{c}) = \beta\frac{e^{-2x}-1+2x}{2x^2}
\end{equation}

\noindent where $T$ is the camera exposure time, $x=T/\tau_{c}$, and $\beta$ is an instrumentation factor that accounts for
speckle sampling, polarization, and coherence effects \cite{Bandyopadhyay:2005bg}. For these measurements, it was assumed that $\beta=1$, which exclusively allows for the computation of relative flow changes. The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).

Because $\tau_c$ is inversely related to the speed of moving scatterers in the sample \cite{Bonner:1981hg}, the inverse correlation time ($ICT = 1/\tau_c$) is commonly used for visualization. In order to compare the LSCI measurements with the flow sensor, the relative flow for each technique was calculated using the average value of the first step (2.4 mm/s) as the baseline. The initial rise of the first flow step was also used to synchronize the timing of the two datasets.

@@

A schematic of the MESI setup is shown in Fig.~\ref{fig:system_mesi}. MESI was performed \cite{Parthasarathy:2008el} using a wavelength-stabilized 785 nm laser diode (LD785-SEV300, Thorlabs, Inc.) mounted in a temperature-controlled housing (TCLDM9, Thorlabs, Inc.) and collimated using an aspheric lens (C280TMD-B, Thorlabs, Inc.). The operating current on the laser diode controller (LDC205C, Thorlabs, Inc.) was fixed at 380 mA (300 mW) and the target temperature set to 25 $^\circ$C on the temperature controller (TED200C, Thorlabs, Inc.). The collimated laser light was passed through a free-space optical isolator (Electro-Optics Technology, Inc.) to minimize back reflections that interfere with single frequency performance. Because the external volume holographic grating of the stabilized laser diode produces a dark spot in the far field, the laser was coupled \textcolor{red}{(Which lens?)} into a single-mode patch cable (P3-780A-FC-2, Thorlabs, Inc.) to obtain a Gaussian beam. The fiber output was re-collimated (F230APC-780, Thorlabs, Inc.), intensity modulated with an acousto-optic modulator (AOM, 3100-125; RF Driver 1110AF-AIFO-1.0, Gooch \& Housego, Ltd.), and relayed to obliquely illuminate the microfluidic.

A pair of consumer camera lenses were used to image the scattered light (AF Nikkor 50 mm $f$/1.8D + AF Micro-Nikkor 105 mm $f$/2.8D, Nikon Corp.) with 2.1$\times$ magnification through a bandpass filter (785$\pm$31 nm, 87-773, Edmund Optics Inc.) to a CMOS camera (acA1920-155um, 1920 $\times$ 1200 pixels, Basler AG). Only a subset of the overall sensor array was used (1000 $\times$ 750 pixels), resulting in a field-of-view of 2.9 $\times$ 2.2 mm. The camera exposures were temporally synchronized with the modulated laser pulses. Fifteen different camera exposures ranging between 50 $\mu$s and 80 ms were recorded for each complete MESI frame, resulting in an effective acquisition rate of approximately 2.5 fps. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The entire acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

% Figure 3 - MESI System Schematic
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
    \caption {
        System schematic for microfluidic flow assessment of MESI and LSCI with the pressure-regulated flow system.
    }
    \label{fig:system_mesi}
\end{figure}

\subsection{MESI and LSCI Performance}

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}. Because the flow sensor software used a separate clock than the MESI acquisition, the datasets were synchronized during post-processing using the initial rise of the first flow step. The experiment was repeated a total of four times across two days.

The raw intensity images were converted to speckle contrast images and the average value within the microfluidic channel extracted from each frame as described in Section \ref{sect:methods_lsci}. The average speckle contrast values from all fifteen exposure times were then fitted to the multi-exposure speckle visibility equation \cite{Parthasarathy:2008el} to obtain an estimate of $\tau_c$,
%
% Equation 6 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K^2(T,\tau_c) =
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu
\end{equation}

\noindent where $T$ is the camera exposure time, $x=T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu$ represents exposure-independent instrument noise and nonergodic variances. $\beta$ was held constant at all timepoints during an experiment by performing an initial fit to Eq. \ref{eq:mesi} using the median speckle contrast value at each exposure across the entire multi-exposure dataset. All fitting was performed with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in MATLAB (R2021a, MathWorks, Inc.). The resulting $\tau_c$ estimates were resampled to 2 Hz using interpolation and smoothed temporally with a central moving average filter ($k=5$).

In order to directly compare the MESI and single-exposure LSCI measurements with the flow sensor, the relative flow was calculated using the average value of the first step (1 mm/s) as the baseline. The average values for each flow step were calculated using 115 seconds of data, allowing for 5 seconds of transition from the previous step.

@@

The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor is shown in Fig.~\ref{fig:SvP-FS}. These plots demonstrate that the pressure-regulated system outperforms the syringe pump by accurately and steadily matching the programmed flow speeds across both experiments. While both flow systems responded quickly to the desired flow changes during the large step size experiment (Fig.~\ref{fig:SvP-FS}a), the syringe pump system suffered from accuracy and stability issues compared to the pressure-regulated system. Furthermore, the small step size experiment (Fig.~\ref{fig:SvP-FS}b) demonstrated that the syringe pump system could not reliably reproduce the finer flow changes as evidenced by the loss of the stair-stepped flow pattern.

% Figure 4 - Syringe Pump vs. Pressure System (Flow Sensor only)
\begin{figure}
    \includegraphics[width=\textwidth]{Figure4.pdf}
    \caption {
        Flow sensor measurements for the syringe pump (blue) and pressure-regulated (red) flow systems compared to the ideal programmed flow (black) for one run of the (a) 3-step and (b) 13-step experiments. The microfluidic flow speed varied between 2.4 to 4.8 mm/s in 1.2 mm/s and 0.2 mm/s steps for the 3- and 13-step experiments, respectively.
    }
    \label{fig:SvP-FS}
\end{figure}

Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiment. These results confirm the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds. The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}. These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes. With the syringe pump system, it would be impossible to reliably separate changes in relative flow of 20\% from flow system noise at the 2.4 mm/s flow speed. This magnitude of uncertainty in flow generation would make it difficult to assess an optical system's ability to detect small changes in flow. This limitation is visually represented in Fig.~\ref{fig:SvP-FS}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes. Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.5\% while remaining confident that the resulting optical system measurements were not caused by flow system noise. This level of certainty would also permit assessing improvements to optical system performance at this scale.

@@

\subsection{LSCI Flow Measurements}

The comparison between the syringe pump and the pressure-regulated flow systems as measured with the inline flow sensor and LSCI is shown in Fig.~\ref{fig:SvP-FS_LSCI}. The underlying data for both plots are the same as in Fig.~\ref{fig:SvP-FS}b but are normalized against the first flow step. The relative flow changes measured by LSCI closely track those of the flow sensor and corroborate the accuracy and stability issues seen with the syringe pump system. These results also demonstrate that LSCI is capable of detecting similar changes in flow as the commercial flow sensor for relative flow changes up to double the baseline \textcolor{red}{(awkward wording)}.

% Figure 5 - Syringe Pump vs. Pressure System (Flow Sensor + LSCI)
\begin{figure}
    \includegraphics[width=\textwidth]{Figure5.pdf}
    \caption {
        Relative flow measurements for the (a) syringe pump and (b) pressure-regulated flow systems as measured with the flow sensor (blue) and single-exposure LSCI (red). All measurements were normalized to the average of the first flow step (2.4 mm/s) and compared to the ideal programmed flow (black).
    }
    \label{fig:SvP-FS_LSCI}
\end{figure}

\subsection{MESI and LSCI Performance}
